Kelompok 4_Praktikum_Pekan 8

### 2024-04-07 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r}
sample_sizes <- c(4, 12, 20, 60, 100)

sample_and_plot <- function(data, n) {
  sample_data <- sample(data, n)

  hist(sample_data, main = paste("Histogram (n =", n, ")"), 
       xlab = "Value", ylab = "Frequency", col = "#8DC16D")

  qqnorm(sample_data, main = paste("Normal QQ Plot (n =", n, ")"), 
         xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
  qqline(sample_data)
}

for (n in sample_sizes) {
  cat("Ukuran sampel n =", n, "\n")

  cat("Data dari sebaran normal:\n")
  sample_and_plot(norm_data, n)
  cat("\n")

  cat("Data campuran:\n")
  sample_and_plot(mixed_data_3, n)
  cat("\n\n")
}
```

@@

>>>>

@@

s
